Discrete Time Markov Model

### 2025-04-09 analysis/discrete-markov.qmd
Updating DS model

```{r long_data}
data_stack <- data_stack |>
  inner_join(data[, cols], by = "ID") |>
  pivot_and_factorise() |>
  group_by(ID) |>
  mutate(Age = Age - (2022 - as.numeric(as.character(wave))))

>>>>

```{r long_data}
data_stack <- data_stack |>
  inner_join(data[, cols], by = "ID") |>
  pivot_and_factorise() |>
  group_by(ID) |>
  mutate(Age = Age - (2022 - as.numeric(as.character(wave)))) |>
  select(!starts_with("Cardio") & !starts_with(paste0("Total_dep_20", 18:22)))
